Fig3

### 2020-05-13 analysis/02_DESeq2.Rmd
not working...

```{r setup}
library(tidyverse)
library(DESeq2)
library(BiocParallel)
register(MulticoreParam(6))
library(caret)  # for sampling data
library(cowplot)

@@

## Characterization

```{r readfiles, eval=T}
# import "colData" which contains sample information and "countData" which contains read counts
countData <- read.csv("../results/00_countData_characterization.csv", header = T, row.names = 1)
geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)
head(geneinfo)

# craete variable that will be critical for subset later on
colData <- read.csv("../metadata/00_colData_characterization.csv", header = T, row.names = 1)
colData$sextissue <- as.factor(paste(colData$sex, colData$tissue, sep = "_"))
colData$treatment <- factor(colData$treatment, levels = charlevels)
colData$tissue <- factor(colData$tissue, levels = tissuelevel)
levels(colData$treatment)
levels(colData$sex)
levels(colData$sextissue)
levels(colData$tissue)
```

```{r deseq2, eval=F, include=F}
for(i in levels(colData$sextissue)){

  myfilename = paste0("../results/DEseq2/", i, "_vsd.csv")
  write.csv(vsd, myfilename)

  #return(dds)
  #return(vsd)
  print(head(vsd))

  # save differential gene expression results
  control.bldg <- createDEGdfsave("bldg", "control", i)
  bldg.lay <- createDEGdfsave("lay", "bldg", i)
  lay.inc.d3 <- createDEGdfsave("inc.d3", "lay",  i) 
  inc.d3.inc.d9 <- createDEGdfsave("inc.d9", "inc.d3", i) 
  inc.d9.inc.d17 <- createDEGdfsave("inc.d17", "inc.d9", i)
  inc.d17.hatch <- createDEGdfsave( "hatch", "inc.d17", i) 
  hatch.n5 <- createDEGdfsave( "n5", "hatch",  i) 
  n5.n9 <- createDEGdfsave("n9", "n5",  i) 
}

## Manipulation

### Data wrangle

```{r manipulation1, eval = F, include = F}
# import "colData" which contains sample information and "countData" which contains read counts
countData <- read.csv("../results/00_counts.csv", header = T, row.names = 1)
geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)
head(geneinfo)

levelsreplace <- c( "m.inc.d8" , "prolong" , "extend")
levelsremoval <- c( "m.inc.d3" ,    "m.inc.d9" , "m.inc.d17" , "m.n2")
controlsremovalreplace <- c( "inc.d3" ,    "inc.d9" , "inc.d17" , "hatch")

manipulationsandcontrols <- c(controlsremoval, levelsreplace, levelsremoval)

colData <- read.csv("../metadata/00_samples.csv", header = T, row.names = 1)
colData$sextissue <- as.factor(paste(colData$sex, colData$tissue, sep = "_"))
colData$treatment <- factor(colData$treatment, levels = manipulationsandcontrols)
colData$tissue <- factor(colData$tissue, levels = tissuelevel)
levels(colData$treatment)
levels(colData$sex)
levels(colData$sextissue)
levels(colData$tissue)
colData <- colData %>% drop_na()
```
### Manipuation: comparisons to respective controls

```{r manipulationcontrol, eval = F}

createDEGdfsaveManip <- function(up, down, mytissue){

  partialfilename = paste("_", down, "_", up, sep = "")
  myfilename = paste0("../results/DESeq2/manip/", mytissue, partialfilename, "_DEGs.csv")

  myfilename = paste0("../results/DEseq2/manip/", i, "_vsd.csv")
  write.csv(vsd, myfilename)

  # save differential gene expression results
  inc.d3.m.inc.d3 <- createDEGdfsaveManip("m.inc.d3", "inc.d3",  i) 
  inc.d9.m.inc.d9 <- createDEGdfsaveManip("m.inc.d9", "inc.d9",  i) 
  inc.d17.m.inc.d17 <- createDEGdfsaveManip("m.inc.d17", "inc.d17",  i) 
  hatch.m.n2 <- createDEGdfsaveManip("m.n2", "hatch",  i) 
  inc.d9.m.inc.d8 <- createDEGdfsaveManip("m.inc.d8", "inc.d9",  i) 
  inc.d17.prolong <- createDEGdfsaveManip("prolong", "inc.d17",  i) 
  hatch.extend <- createDEGdfsaveManip("extend", "hatch",  i) 
}

## Manipulation: comparisons to other manipluations

```{r manipulationwithin, eval = F}
# import "colData" which contains sample information and "countData" which contains read counts
countData <- read.csv("../results/00_counts.csv", header = T, row.names = 1)
geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)
head(geneinfo)

levelsreplace <- c( "m.inc.d8" , "prolong" , "extend")
levelsremoval <- c( "m.inc.d3" ,    "m.inc.d9" , "m.inc.d17" , "m.n2")
controlsremovalreplace <- c( "inc.d3" ,    "inc.d9" , "inc.d17" , "hatch")

manipulationsandcontrols <- c(controlsremoval, levelsreplace, levelsremoval)

colData <- read.csv("../metadata/00_samples.csv", header = T, row.names = 1)
colData$sextissue <- as.factor(paste(colData$sex, colData$tissue, sep = "_"))
colData$treatment <- factor(colData$treatment, levels = manipulationsandcontrols)
colData$tissue <- factor(colData$tissue, levels = tissuelevel)
levels(colData$treatment)
levels(colData$sex)
levels(colData$sextissue)
levels(colData$tissue)
colData <- colData %>% drop_na()

createDEGdfsaveManip <- function(up, down, mytissue){

  partialfilename = paste("_", down, "_", up, sep = "")
  myfilename = paste0("../results/DESeq2/manip/", mytissue, partialfilename, "_DEGs.csv")

  myfilename = paste0("../results/DEseq2/manip/", i, "_vsd.csv")
  write.csv(vsd, myfilename)

  # save differential gene expression results
  hatch.m.n2 <- createDEGdfsaveManip("m.n2", "hatch",  i) 
  prolong.extend <- createDEGdfsaveManip("extend", "prolong",  i) 
  early.extend <- createDEGdfsaveManip("extend", "m.inc.d8",  i) 
  early.prolong <- createDEGdfsaveManip("prolong", "m.inc.d8",  i) 
  m.inc.d9.m.inc.d3 <- createDEGdfsaveManip("m.inc.d9", "m.inc.d3",  i) 
  m.inc.d17.m.inc.d9 <- createDEGdfsaveManip("m.inc.d17", "m.inc.d9",  i) 
  m.inc.d17.m.inc.d3 <- createDEGdfsaveManip("m.inc.d17", "m.inc.d3",  i) 
  m.n2.m.inc.d17 <- createDEGdfsaveManip("m.n2", "m.inc.d17",  i) 
  m.n2.m.inc.d9 <- createDEGdfsaveManip("m.n2", "m.inc.d9",  i)
  m.n2.m.inc.d3 <- createDEGdfsaveManip("m.n2", "m.inc.d3",  i)
  prolong.m.inc.d17 <- createDEGdfsaveManip("prolong", "m.inc.d17",  i) 
  m.inc.d8.m.inc.d9 <- createDEGdfsaveManip("m.inc.d8", "m.inc.d9",  i) 
  extend.m.n2 <- createDEGdfsaveManip("extend", "m.n2",  i) 
}

>>>>

```{r setup}
library(tidyverse)
library(DESeq2)
library(BiocParallel)
register(MulticoreParam(6))
library(cowplot)

@@

### 2020-05-13 analysis/03_DESeq2part2.Rmd
not working...

@@

```{r write}
write.csv(hypothesisDEGs, "../results/03_hypothesisDEGs.csv")
write.csv(allDEG, "../results/03_allDEGs.csv")
write.csv(candidatevsd, "../results/03_candidatevsd.csv")
```

>>>>

## WGCNA

```{r WGCNA}
## genes WGCNA prl module

WGCNAgenes <- read_csv("../results/04_PRLmodule.csv") %>% pull(x)
WGCNAvsd <- getcandidatevsd(WGCNAgenes, "pituitary", sexlevels) 
```

@@

```{r write}
write.csv(hypothesisDEGs, "../results/03_hypothesisDEGs.csv")
write.csv(allDEG, "../results/03_allDEGs.csv")
write.csv(candidatevsd, "../results/03_candidatevsd.csv")
write.csv(WGCNAvsd, "../results/03_WGCNAvsd.csv")

### 2020-05-13 analysis/figure-3.Rmd
not working...

source("../R/datawrangling.R")

@@

```{r}
candidatevsd <- read_csv("../results/03_candidatevsd.csv")
head(candidatevsd)

@@

```{r}
## genes WGCNA prl module

WGCNAgenes <- read_csv("../results/PRLmodule.csv") %>% pull(x)

WGCNAvsd <- getcandidatevsd(WGCNAgenes, "pituitary", sexlevels)

@@

candidatevsd <- getcandidatevsd(hypothesisDEGs, "pituitary", sexlevels)

>>>>

@@

```{r PRLpit}
candidatevsd <- read_csv("../results/03_candidatevsd.csv")
head(candidatevsd)

@@

```{r WGCNA}
## genes WGCNA prl module

WGCNAgenes <- read_csv("../results/04_PRLmodule.csv") %>% pull(x)
WGCNAvsd <- read_csv("../results/03_WGCNAvsd.csv")
```

@@

candidatevsd <-read_csv("../results/03_candidatevsd.csv")
